Proposal to improve BBC Search through the use of Linked Data

### 2014-05-06 chapter3.tex
Added more to chapter 3
Slow progress with chapter3 and moved some stuff from chapter 1 as that's still too long.

\subsection{The Content}

The front end search application currently divides all the searchable
content into so-called ``zones'',

@@

@@

@@

>>>>

\subsection{The Content}
\label{content}

The front end search application currently divides all the searchable
content into so-called ``zones''. Table~\ref{zones-table}

%TODO - is this all of them?
\begin{table}[h]
\begin{tabular}{| l | l |}
  Zone/Category          & Notes/Comments \\
  \hline
  About the BBC          &  Static pages, blogs, articles. RSS/Atom feeds available. \\
  Blogs                  &  Legacy blog content. RSS/Atom available. \\
  CBBC                   &  Pages, games, programmes information for Children. Some semantic markup exists for Facebook's Open Graph. \\
  Films                  &  Legacy site for BBC Film Network and current site for BBC Films. Little semantic markup. \\
  Food                   &  Recipes features on BBC programmes. No semantic markup despite sister website BBC Good Food website using Schema.org microdata. \\
  Gardening              &  Legacy website not updated since 2006. All static HTML content with no semantic markup. \\
  Health \& Parenting    &  \\
  History                &  \\
  iPlayer                &  \\
  Learning               &  \\
  Local (archive)        &  \\
  Music                  &  \\
  News                   &  \\
  Ouch!                  &  \\
  Religion \& Ethics     &  \\
  Science \& Nature      &  \\
  Sport                  &  \\
  Teenagers              &  \\
  TV \& Radio Programmes &  \\
  TV \& Radio Sites      &  \\
\end{tabular}
\caption{Categories or ``zones'' of content currently indexed by BBC Search.}
\label{zones-table}
\end{table}

Some of these zones or categories are related to major, well-known areas of
BBC online. Some seem to be more esoteric or legacy areas, many of which
are obtained through a web crawler. The presence of ``iPlayer'',
``TV \& Radio Programmes'' and ``TV \& Radio Sites'' is a distinction that
has arisen for technical and historic reasons, which is not likely to be
clear to users.

There is a wealth of legacy content that is likely to be obtainable only by
crawling. Some active sites are syndicated via RSS/Atom, but a subscription-based
feed does not allow indexing a backfill of content easily.

@@

The default results page currently returned for a query breaks the individual
results into the zones or categories mentioned in section~\ref{content}. A
navigation menu on the left allows users to drill down into the results just
for that category.

@@

Each and every link promoted within this feature is hand-chosen by editorial
staff and much manual effort is needed to keep promoting new concepts
as they appear and to remove pages as they get superseded. It is hoped
in this proposal we can reduce some of that manual curation through the use
of linked data and demonstrate ways editorial staff can focus on curating
their own linked data such that Editor's Choice could evolve into a more
generalised and automated subsystem. A metadata-driven curation system
could use common patterns in the data to promote orders of magnitude more
top links with a fraction of the current effort.

@@

The list of suggestions that might surface in this system are
currently chosen and maintained by hand by editorial staff. If a new
concept breaks into the news (such as a notable person becoming notable
for the first time), then a person must enter that term into the system.
Similarly, if something should not be suggested to users any longer
(perhaps for legal reasons or simply because it is no longer a relevant
concept), then it must be amended or removed manually.

This manual maintenance of the suggestion list also leads to a
disconnect between searchable content and suggested queries that might
appear as users type. There is an onus on editorial staff to ensure
that content will be found when a suggested query is used. It might
serve the website users better to find mechanisms by which to generate
a useful set of suggestions from the corpus of content as it is
indexed. The heterogenous nature of BBC content turns this into
further integration work where different business rules are likely required
to generate suggestions from different types of content.
